---
title: "Workpackage I: Schools"
#author: "Simon Calmar Andersen"
#date: "2022-11-12"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true



---


Project leader on the Immgrant work package is Jakob Majlund Holm

# Description

The aim of Workpackage I: Schools is to study what factors influence schools' decision to adopt and implement a new program.

## Interventions

We test several interventions.

### Focus of first invitation

In the first invitation to schools send out by email, we randomly assigned schools to two versions of the invitation.

# Preregistration

An anomymized version of the preregistration can be found [here](https://aspredicted.org/5JK_RG9)


# Power calculation

We did the following power calculation before the beginning of the intervention.

```{r, echo=FALSE}
library(pwr)
```

```{r, echo=TRUE}
power_schools <- power.prop.test(n= 200,
           p1 = 0.30,
           sig.level = 0.05,
           power = 0.80)
power_schools
```
which shows that with share of signup of `r power_schools$p1` in the baseline condition we need `r power_schools$p2` in the treatment condition, and thereby a minimum detectable effect size of `r power_schools$p2 - power_schools$p1`.